Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface

### 2022-07-23 main.tex
:pencil: Add simulation results

% glossaries-extra
\setabbreviationstyle[acronym]{long-short}
\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
\newacronym{dtmac}{DTMAC}{Discrete Thresholding Multiple Access Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{irs}{IRS}{Intelligent Reflecting Surface}
\newacronym{kkt}{KKT}{Karush–Kuhn–Tucker}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pgd}{PGD}{Projected Gradient Descent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{ue}{UE}{user}
\newacronym{wit}{WIT}{Wireless Information Transfer}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
\newacronym{wpt}{WPT}{Wireless Power Transfer}

@@

\begin{section}{Simulation Results}
	In this section, we provide numerical results to evaluate the proposed input, beamforming and decision design over a single-user multi-node Metascatter-enabled network.
	We assume the distance between \gls{ap} and user is \SI{10}{\meter}, and $K=2$ Metascatters are uniformly dropped within a disk of radius \SI{1}{\meter} centered at the user.
	% The carrier frequency is $f=\SI{200}{\MHz}$, and we consider \gls{iid} Ricean fading for all channels.
	The carrier frequency is $f=\SI{200}{\MHz}$, and we consider \gls{iid} Ricean fading between all terminals.
	For direct, forward and backward links, the path loss exponents are \num{2.6}, \num{2.4} and \num{2}, while the Ricean factor are \num{5}, \num{5} and \num{10}, respectively.
	% For direct, forward and backward links, we choose path loss exponents \num{2.6}, \num{2.4} and \num{2}, and Ricean factor \num{5}, \num{5} and \num{10}, respectively.
	% and the path loss exponents for direct, forward and backward links are \num{2.6}, \num{2.4} and \num{2}, respectively.
	% We consider \gls{iid} Ricean fading for all channels with Ricean factor set to \num{5}, \num{5} and \num{10}
	The \gls{ap} has $Q=4$ antennas with maximum average transmit power $P=\SI{36}{\dBm}$.
	All node perform \gls{qam} with $M=2$ input states, the amplitude reflect ratio is $\alpha=0.5$, and the symbol period ratio is $N=20$.
	% and we consider amplitude reflect ratio $\alpha=0.5$ and symbol period ratio $N=20$.
	% The user has a receive antenna gain of \SI{3}{\dBi} and average noise power
	The user is with average noise power $\sigma_v^2=\SI{70}{\dBm}$ and receive antenna gain \SI{3}{\dBi}.
	All rate regions are averaged over \num{1000} instances.
	% Each node has $M=2$ candidate input states with amplitude reflect ratio $\alpha=0.5$.
	The parameters remain fixed unless otherwise specified.

	\begin{figure}[!t]
		\centering
		\subfloat[Instance 1]{
			\resizebox{0.48\columnwidth}{!}{
				\input{assets/simulation/distribution_weights_1.tex}
			}
		}
		\subfloat[Instance 2]{
			\resizebox{0.48\columnwidth}{!}{
				\input{assets/simulation/distribution_weights_2.tex}
			}
		}
		\caption{Input distribution vs weight $\rho$.}
	\end{figure}

	% \begin{figure}[!t]
	% 	\centering
	% 	\resizebox{0.8\columnwidth}{!}{
	% 		\input{assets/simulation/distribution_weights.tex}
	% 	}
	% 	\caption{1}
	% 	% \caption{Average primary-(total-)backscatter rate region.}
	% \end{figure}
	% \begin{table}[t!]
	% 	\centering
	% 	\caption{Parameters in simulation}
	% 	\begin{tabular}{ll}
	% 		Transmit antenna $Q$     & 1   \\
	% 		Tags $K$                 & 2   \\
	% 		States $M$               & 2   \\
	% 		Reflect ratio $\alpha$   & 0.5 \\
	% 		Duration ratio $N$       & 10  \\
	% 		Noise power $\sigma_v^2$ & 1   \\
	% 		Discretization bins      & 256
	% 	\end{tabular}
	% 	\label{ta:parameters}
	% \end{table}
	% Table \ref{ta:parameters} shows the parameters used in simulation.
	% We assume all links are in standard \gls{cscg} distribution and evaluated the rate regions on two instances.
	% For the input design, ``Cooperation'' assumes full transmit cooperation at all tags (i.e., joint encoding), ``Exhaustion'' runs exhaustive search on all possible input distributions, ``\gls{kkt}'' is proposed \gls{kkt} input design \eqref{eq:input_kkt_solution}, and ``Marginalization'' marginalizes the joint input array by ``Cooperation'' to obtain independent tag input distribution.
	% For the threshold design, ``\gls{smawk}'' refers to the \gls{dp}-based quantization proposed in \cite{He2021}, ``Bisection'' sequentially optimizes each threshold by bisection \cite{Nguyen2020a}, and ``\gls{ml}'' is the \gls{ml} detector that requires no knowledge of input distribution.

>>>>

% glossaries-extra
\setabbreviationstyle[acronym]{long-short}
\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{cp}{CP}{Canonical Polyadic}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
\newacronym{dtmac}{DTMAC}{Discrete Thresholding Multiple Access Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{irs}{IRS}{Intelligent Reflecting Surface}
\newacronym{kkt}{KKT}{Karush–Kuhn–Tucker}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pgd}{PGD}{Projected Gradient Descent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{ue}{UE}{user}
\newacronym{wit}{WIT}{Wireless Information Transfer}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
\newacronym{wpt}{WPT}{Wireless Power Transfer}

@@

\begin{section}{Simulation Results}
	% TODO add distribution to initializer to smooth curves?
	% TODO compare PGD and primary-MRT beamformers
	In this section, we provide numerical results to evaluate the proposed input, beamforming and decision design over a single-user multi-node Metascatter-enabled network.
	We assume the distance between \gls{ap} and user is \SI{10}{\meter}, and $K=2$ Metascatters are uniformly dropped within a disk centered at the user of radius \SI{1}{\meter}.
	% The carrier frequency is $f=\SI{200}{\MHz}$, and we consider \gls{iid} Ricean fading for all channels.
	The carrier frequency is $f=\SI{200}{\MHz}$, and we consider \gls{iid} Ricean fading between all terminals.
	For direct, forward and backward links, we set the path loss exponents to \num{2.6}, \num{2.4} and \num{2}, and the Ricean factor to \num{5}, \num{5} and \num{10}, respectively.
	% For direct, forward and backward links, we choose path loss exponents \num{2.6}, \num{2.4} and \num{2}, and Ricean factor \num{5}, \num{5} and \num{10}, respectively.
	% and the path loss exponents for direct, forward and backward links are \num{2.6}, \num{2.4} and \num{2}, respectively.
	% We consider \gls{iid} Ricean fading for all channels with Ricean factor set to \num{5}, \num{5} and \num{10}
	The \gls{ap} has $Q=4$ antennas with maximum average transmit power $P=\SI{36}{\dBm}$.
	All nodes have amplitude reflect ratio $\alpha=0.5$, symbol period ratio $N=20$, and perform \gls{qam} with $M=2$ input states.
	% and we consider amplitude reflect ratio $\alpha=0.5$ and symbol period ratio $N=20$.
	% The user has a receive antenna gain of \SI{3}{\dBi} and average noise power
	The user is with average noise power $\sigma_v^2=\SI{70}{\dBm}$ and receive antenna gain \SI{3}{\dBi}.
	All rate regions are averaged over at least \num{1000} instances, where ``PSP'' and ``BSP'' means primary and backscatter symbol periods, respectively.
	We choose decision design by \gls{smawk} \cite{He2021} as reference, and select discretize boundaries uniformly over the \qty{95}{\percent} confidence region of edge hypotheses.
	The parameters remain fixed unless otherwise specified.

	\begin{subsection}{Input Distribution vs. Weight}
		\begin{figure}[!t]
			\centering
			\subfloat[Instance 1\label{fi:distribution_weights_1}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/distribution_weights_1.tex}
				}
			}
			\subfloat[Instance 2\label{fi:distribution_weights_2}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/distribution_weights_2.tex}
				}
			}
			\caption{Typical input distributions vs. weight $\rho$ for a Metascatter with $M=4$ inputs.}
			\label{fi:distribution_weights}
		\end{figure}
		% We consider a single Metascatter with $M=4$ inputs in this case of study.
		In Fig. \ref{fi:distribution_weights}, we present typical input distributions of a single Metascatter with $M=4$ inputs under different weight $\rho$.
		Fig. \subref*{fi:distribution_weights_1} and \subref*{fi:distribution_weights_2} are obtained from \gls{iid} drop and channel realizations.
		We note that even for $\rho=0$ (i.e., best backscatter performance), the optimal input distribution is not equiprobable like \gls{sr}, and adaptive channel coding can further increase total backscatter rate based on \gls{csi}.
		On the other hand, the optimal input distribution becomes fully deterministic at $\rho=1$ (i.e., best primary performance), where the state maximizes equivalent primary channel \eqref{eq:equivalent_channel} strength is chosen with probability \num{1}.
		In this case, Metascatter boils down to an \gls{irs} element with $M$ discrete states.
		As $\rho$ moves from \num{0} to \num{1}, the optimal input distribution becomes gradually biased to one state and flexibly balances the primary-backscatter tradeoff.
	\end{subsection}

	\begin{subsection}{Rate Region vs. Input, Beamforming, and Decision Schemes}
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution\label{fi:region_distribution}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_distribution.tex}
				}
			}
			\subfloat[Decision Threshold\label{fi:region_threshold}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_threshold.tex}
				}
			}
			\caption{Average primary-(total-)backscatter rate regions for different input distribution and decision threshold schemes.}
		\end{figure}
		Fig. \subref*{fi:region_distribution} compares the achievable rate regions by following input designs.
		\begin{itemize}
			% \item ``Exhaustion'' means $K$-dimensional grid search over probability simplex;
			% \item ``\gls{kkt}'' corresponds to Algorithm \ref{al:input_distribution};
			% \item ``Cooperation'' assumes backscatter cooperation/joint encoding at all Metascatters, and employs Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a} to determine \emph{tuple} input distribution;
			\item \textbf{Exhaustion:} $K$-dimensional grid search over probability simplex;
			\item \textbf{\gls{kkt}:} results of Algorithm \ref{al:input_distribution};
					% \item \textbf{Cooperation:} with backscatter cooperation/joint encoding at all Metascatters, Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a} for \emph{tuple} input distribution;
					% \item \textbf{Cooperation:} backscatter cooperation/joint encoding at all Metascatters, \emph{tuple input distribution} by Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a};
					% \item \textbf{Cooperation:} with backscatter cooperation (i.e., joint encoding) at all Metascatters, \emph{tuple input distribution} by Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a};
			\item \textbf{Cooperation:} backscatter cooperation/joint encoding at all Metascatters, tuple input distribution/joint probability array optimization by Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a};
					% with backscatter cooperation (i.e., joint encoding) at all Metascatters, \emph{tuple input distribution} by Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a};
			\item \textbf{Marginalization:} marginal distributions of joint probability array;
			\item \textbf{Decomposition:} normalized tensors of rank-1 \gls{cp} decomposition of joint probability array;
			\item \textbf{Randomization:} Gaussian recovery from joint probability array \cite{Calvo2010}.
		\end{itemize}

		We notice adaptive joint encoding at all Metascatters provides the outer bound of rate region.
		However, it involves arbitrarily dependent codewords, and backscatter cooperation between passive nodes is generally unaffordable.
		In contrast, the rate region of \gls{kkt} input design in Algorithm \ref{al:input_distribution} approaches that of exhaustive search, and the loss is negligible for $K=2$.
		% Although the randomization method \cite{Calvo2010} achieves similar performance, the computational complexity is much higher as it involves solving $K+1$ linear programming problems
		Although the randomization method \cite{Calvo2010} returns similar rate region, it requires solving $K+1$ linear programming problems before applying Gaussian recovery.
		The marginal distribution is slightly worse than \gls{kkt} despite having the same computational complexity, while the approximation from \gls{cp} decomposition is unsatisfying.

		% TODO: beamforming

		Fig. \subref*{fi:region_threshold} compares the achievable rate region by following threshold schemes.
		\begin{itemize}
			\item \textbf{\gls{dp}:} sequential quantizer grouping by dynamic programming \cite{He2021};
			\item \textbf{\gls{smawk}:} above accelerated by \gls{smawk} algorithm;
			\item \textbf{Bisection:} sequential bisection threshold design \cite{Nguyen2020a};
			\item \textbf{\gls{ml}:} maximum likelihood decision \eqref{eq:detection_threshold_maximum_likelihood} \cite{Qian2019}.
		\end{itemize}

		We observe that input-adaptive threshold designs achieve higher total backscatter rate than \gls{ml}.
		This is because the decision regions can be flexibly adjusted to enhance the capacity of \gls{dtmac} \eqref{eq:dtmac}.
		For example, the tuples with negligible input probability should have narrower decision regions than those frequently employed, in order to improve detection performance.
		It emphasizes the importance of joint input distribution and decision region design.

		% We note that ideal joint adaptive encoding at all Metascatters can further boost the total backscatter rate.
		% However, this ideal upper bound requires real-time feedback
		% ``Exhaustion'' means $K$-dimensional grid search over probability simplex, ``KKT'' corresponds to Algorithm \ref{ap:input_kkt_solution}, ``Cooperation'' assumes full backscatter cooperation and joint encoding at all Metascatters
	\end{subsection}

	\begin{subsection}{Rate Region vs. System Configuration}
		\begin{figure}[!t]
			\centering
			\subfloat[Metscatter Nodes\label{fi:region_tags}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_tags.tex}
				}
			}
			\subfloat[Input States\label{fi:region_states}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_states.tex}
				}
			}
			\\
			\subfloat[Transmit Antennas\label{fi:region_txs}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_txs.tex}
				}
			}
			\subfloat[Scatter Ratio\label{fi:region_scatter}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_scatter.tex}
				}
			}
			\caption{Average primary-(total-)backscatter rate regions.}
			\label{fi:region_config_1}
		\end{figure}

		% Fig. \ref{fi:region_config_1} reveals the impact of Metascatter nodes, input states, transmit antennas and scatter ratio on the achievable rate region.
		We present in \ref{fi:region_config_1} the impact of Metascatter nodes, input states, transmit antennas and scatter ratio on the achievable rate region.
		For the specified scenario, Fig. \subref*{fi:region_tags} shows the total backscatter rate almost scales proportionally with the number of Metascatter nodes, and the decrease of individual backscatter rate is unobvious.
		Besides, we conclude from \subref*{fi:region_states} that increasing the reflection states has a marginal effect on both primary and backscatter rates.
		Those two facts motivates the use of numerous elementary/uncomplicated backscatter nodes, instead of high-order transponders or programmable high-resolution surfaces.
		Figs. \subref*{fi:region_txs} and \subref*{fi:region_scatter} also prove increasing transmit antennas or scatter ratio can improve both primary and backscatter performance.

		\begin{figure}[!t]
			\centering
			\subfloat[User Coverage\label{fi:region_coverage}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_coverage.tex}
				}
			}
			\subfloat[Symbol Period Ratio\label{fi:region_duration}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_duration.tex}
				}
			}
			\\
			\subfloat[Carrier Frequency\label{fi:region_frequency}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_frequency.tex}
				}
			}
			\subfloat[Average Noise Power\label{fi:region_noise}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_noise.tex}
				}
			}
			\caption{Average primary-(total-)backscatter rate regions.}
			\label{fi:region_config_2}
		\end{figure}
	\end{subsection}
	% \begin{figure}[!t]
	% 	\centering
	% 	\resizebox{0.8\columnwidth}{!}{
	% 		\input{assets/simulation/distribution_weights.tex}
	% 	}
	% 	\caption{1}
	% 	% \caption{Average primary-(total-)backscatter rate region.}
	% \end{figure}
	% \begin{table}[t!]
	% 	\centering
	% 	\caption{Parameters in simulation}
	% 	\begin{tabular}{ll}
	% 		Transmit antenna $Q$     & 1   \\
	% 		Tags $K$                 & 2   \\
	% 		States $M$               & 2   \\
	% 		Reflect ratio $\alpha$   & 0.5 \\
	% 		Duration ratio $N$       & 10  \\
	% 		Noise power $\sigma_v^2$ & 1   \\
	% 		Discretization bins      & 256
	% 	\end{tabular}
	% 	\label{ta:parameters}
	% \end{table}
	% Table \ref{ta:parameters} shows the parameters used in simulation.
	% We assume all links are in standard \gls{cscg} distribution and evaluated the rate regions on two instances.
	% For the input design, ``Cooperation'' assumes full transmit cooperation at all tags (i.e., joint encoding), ``Exhaustion'' runs exhaustive search on all possible input distributions, ``\gls{kkt}'' is proposed \gls{kkt} input design \eqref{eq:input_kkt_solution}, and ``Marginalization'' marginalizes the joint input array by ``Cooperation'' to obtain independent tag input distribution.
	% For the threshold design, ``\gls{smawk}'' refers to the \gls{dp}-based quantization proposed in \cite{He2021}, ``Bisection'' sequentially optimizes each threshold by bisection \cite{Nguyen2020a}, and ``\gls{ml}'' is the \gls{ml} detector that requires no knowledge of input distribution.
